Starting Populations Summary Stats

### 2022-05-30 FEM_R/FEM_ALL_PLOTS_AND_ANALYSES.Rmd
Lots of WIP and changes for the lockdown_alcohol intervention

---
title: "R Notebook"
output: html_notebook
---

# Setup

## Libraries
```{r "setup", include=FALSE}
require(tidyverse)
require(haven)
require(ggplot2)
require(Hmisc)
require(reshape2)
theme_set(theme_bw())
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

# Methods

## Summary Stats for Starting Populations

### Function Declaration
```{r}
require(survey)
weighted.survey.means <- function(init.pop, transition=FALSE) {

@@

#### Incidence
```{r}
getIncidenceRate <- function(t, var) {

@@

Handover plots are generated from a Stata script that can be called via a Make rule (`make handovers`). The core_complete set of scenarios must be run prior to this with the `55p_f_l` & `55p_m_l` subpopulations.

@@

## Smoking
```{r}
FEM_base <- read_dta('output/COMPLETE/ELSA_core_base/ELSA_core_base_summary.dta')
# Smoking prevalence stats
smok.5059 <- 15.2
smok.60p <- 10.2
# FEM summary, filter for 2018 and 60p
#FEM.smok <- FEM_sum
FEM.smok <- FEM_base
FEM.smok <- FEM.smok %>%
                filter(year == 2018) %>%
                select(contains('smoken')) %>%
                select(contains('60p'), contains('5059')) %>%
                select(contains('p_'))
FEM.smok <- FEM.smok * 100
smok.combined <- data.frame(FEM = FEM.smok[1,1], ASH = 10.2)
smok.combined <- data.frame(source = c('FEM', 'FEM', 'ASH', 'ASH'), age = c('50 - 59', '60+', '50 - 59', '60+'), value = c(FEM.smok[1,2], FEM.smok[1,1], 15.2, 10.2))
group.colours <- c(FEM = '#00bfc4', ASH = '#f8766d')
smok.plot <-ggplot(data = smok.combined, aes(x = age, y = value)) +
                geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
                scale_fill_manual(values=group.colours) +
                labs(x = ' ', y = 'Prevalence (%)')

@@

## Heart Disease Intervention
```{r echo=FALSE}
# compareDeathAge <- function(base, int, int_name, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {
#   
#   aDeath <- data.frame(base$year, base$d_age_all, int$d_age_all)
#   
#   aDeath <- aDeath %>%
#                 dplyr::rename('Year' = base.year, 'Baseline' = base.d_age_all, !!quo_name(int_name) := int.d_age_all) %>%
#                 reshape2::melt(id.var = 'Year', value.name = 'Age')
#   
#   p1 <- ggplot(data = aDeath, aes(x = Year, y = Age, color = variable)) +
#         geom_smooth(lwd = 0.5, se=FALSE) +
#         labs(x = 'Year', y = 'Age at Death') +
#   
#   if(save) {
#     ggsave(filename = 'hearte_dAge_all.png',
#          plot = p1,
#          path = path)
#   }
#   
#   return(p1)
# }
```

### Life-Expectancy
```{r echo=FALSE}
# b <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_summary.dta')
# h_p <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')
# 
# compareDeathAge(b, h_p, 'No Heart Disease', save=FALSE)
```

#### With Confidence Intervals
```{r}
b_rep <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_by_rep.dta')
h_rep <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_by_rep.dta')
compareDeathAgeConfints <- function(b, i, int_name=FALSE, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

### Split by Activity Level
```{r echo=FALSE}
# b_rep <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_by_rep.dta')
# h_rep <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_by_rep.dta')
# 
# b <- b_rep
# h <- h_rep
# 
# d.exstat1 <- data.frame(b$year, b$rep, b$d_age_exstat1, h$d_age_exstat1)
# d.exstat1 <- d.exstat1 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat1, 'Intervention' = h.d_age_exstat1)
# d.exstat1.pivot <- pivot_longer(d.exstat1,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p1 <- ggplot(data = d.exstat1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
# p1
# 
# d.exstat2 <- data.frame(b$year, b$rep, b$d_age_exstat2, h$d_age_exstat2)
# d.exstat2 <- d.exstat2 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat2, 'Intervention' = h.d_age_exstat2)
# d.exstat2.pivot <- pivot_longer(d.exstat2,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p2 <- ggplot(data = d.exstat2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
#       scale_fill_grey()
# p2
# 
# d.exstat3 <- data.frame(b$year, b$rep, b$d_age_exstat3, h$d_age_exstat3)
# d.exstat3 <- d.exstat3 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat3, 'Intervention' = h.d_age_exstat3)
# d.exstat3.pivot <- pivot_longer(d.exstat3,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p3 <- ggplot(data = d.exstat3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'High', x = 'Year', y = 'Life Expectancy')
# p3
# 
# path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/'
# 
# ggsave(filename = 'hearte_dAge_exstat1.png',
#          plot = p1,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_exstat2.png',
#          plot = p2,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_exstat3.png',
#          plot = p3,
#          path = path)
```

### SplitbyEduc
```{r echo=FALSE}
# b <- b_rep
# h <- h_rep
# 
# d.educ1 <- data.frame(b$year, b$rep, b$d_age_educ1, h$d_age_educ1)
# d.educ1 <- d.educ1 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ1, 'Intervention' = h.d_age_educ1)
# d.educ1.pivot <- pivot_longer(d.educ1,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p1 <- ggplot(data = d.educ1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
# p1
# 
# d.educ2 <- data.frame(b$year, b$rep, b$d_age_educ2, h$d_age_educ2)
# d.educ2 <- d.educ2 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ2, 'Intervention' = h.d_age_educ2)
# d.educ2.pivot <- pivot_longer(d.educ2,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p2 <- ggplot(data = d.educ2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
#       scale_fill_grey()
# p2
# 
# d.educ3 <- data.frame(b$year, b$rep, b$d_age_educ3, h$d_age_educ3)
# d.educ3 <- d.educ3 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ3, 'Intervention' = h.d_age_educ3)
# d.educ3.pivot <- pivot_longer(d.educ3,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p3 <- ggplot(data = d.educ3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'High', x = 'Year', y = 'Life Expectancy')
# p3
# 
# path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/test/'
# 
# ggsave(filename = 'hearte_dAge_educ1.png',
#          plot = p1,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_educ2.png',
#          plot = p2,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_educ3.png',
#          plot = p3,
#          path = path)
```

@@

#### Confidence Intervals
```{r}
compareSurvivalCurveConfints <- function(cohort, intervention, int_name, save=FALSE,
                                 path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

  survivals <- data.frame(cohort$Age, cohort$rep, cohort$Survival, intervention$Survival)

  # Had a small problem when trying to rename using the variable name given as function argument
  # Found solution here: https://stackoverflow.com/questions/49650394/how-to-rename-a-variable-using-a-dynamic-name-and-dplyr
  survivals <- survivals %>%
                 dplyr::rename('Age' = cohort.Age, 'Rep' = cohort.rep, 'Baseline' = cohort.Survival, !!quo_name(int_name) := intervention.Survival) %>%
                 pivot_longer(
                   cols = Baseline:'No Smoking',
                   names_to = 'Source',
                   values_to = 'Life_Exp'
                 )

  p <-ggplot(data = survivals, aes(x=Age, y=Life_Exp, color = Source)) +
        geom_smooth(lwd = 0.5) +
        labs(x = 'Age', y = 'Survival')

  if(save) {
    ggsave(filename = paste0(int_name, '_survival_curve.png'),
         plot = p,
         path = path)
  }

  return(p)
}
c_rep <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_by_rep.dta')
s_rep <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_by_rep.dta')
compareSurvivalCurveConfints(c_rep, s_rep, 'No Smoking', save=TRUE)
```

### Lung Disease Prevalence All
```{r}
c <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_summary.dta')
s <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_summary.dta')
# Calculate age and survival curves
c$Age <- (c$year - 2012) + 50
s$Age <- (s$year - 2012) + 50
c$Survival <- c$m_endpop_all / c$m_endpop_all[1]
s$Survival <- s$m_endpop_all / s$m_endpop_all[1]
d.all <- data.frame(c$Age, c$p_lunge_all, s$p_lunge_all)
d.all <- d.all %>%
                dplyr::rename('Age' = c.Age, 'Baseline' = c.p_lunge_all, 'Intervention' = s.p_lunge_all)
d.all.pivot <- pivot_longer(d.all,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Prevalence')
p1 <- ggplot(data = d.all.pivot, aes(x = Age, y = Prevalence, color = Source)) +
      geom_smooth(lwd = 0.5, se=FALSE) +
      labs(x = 'Age', y = 'Prevalence')
p1
path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results'
#ggsave(filename = 'smok_lunge_all.png',
#         plot = p1,
#         path = path)
```

```{r}
c <- c_rep
s <- s_rep
# Calculate age and survival curves
c$Age <- (c$year - 2012) + 50
s$Age <- (s$year - 2012) + 50
c$Survival <- c$m_endpop_all / c$m_endpop_all[1]
s$Survival <- s$m_endpop_all / s$m_endpop_all[1]
d.all <- data.frame(c$Age, c$rep, c$p_lunge_all, s$p_lunge_all)
d.all <- d.all %>%
                dplyr::rename('Age' = c.Age, 'Rep' = c.rep, 'Baseline' = c.p_lunge_all, 'Intervention' = s.p_lunge_all)
d.all.pivot <- pivot_longer(d.all,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Prevalence')
p1 <- ggplot(data = d.all.pivot, aes(x = Age, y = Prevalence, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(x = 'Age', y = 'Prevalence')
p1
path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results'
ggsave(filename = 'smok_lunge_all.png',
         plot = p1,
         path = path)
```

### Life Years & DFLYS
```{r}
aData <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/input_data/detailed_output/tot/base_treated_merged_smoken_tot_test.dta')
all2 <- aData %>%
          summarise(base.ly = mean(total_lifeyears_basecase), int.ly = mean(total_lifeyears),
                    base.dfly = mean(total_dflys_basecase), int.dfly = mean(total_dflys))
all2
```

#### Split by Education
```{r}
educ2 <- aData %>%
          group_by(educ) %>%
          summarise(base.ly = mean(total_lifeyears_basecase), int.ly = mean(total_lifeyears),
                    base.dfly = mean(total_dflys_basecase), int.dfly = mean(total_dflys))
educ2
```

# Comparing Output Values
```{r}
b <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/output/SCENARIO/ELSA_core_base/ELSA_core_base_summary.dta')
h <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')
new.df <- data.frame(b$year, b$d_age_all, h$d_age_all)
new.df$diff <- new.df$h.d_age_all - new.df$b.d_age_all
new.df
```

>>>>

---
title: "FEM_All_plots_and_analyses"
output: html_notebook
---

This notebook holds all the plots and analyses that have been undertaken using the FEM, including many different avenues of validation and results.

# SETUP
## Libraries
```{r "setup", include=FALSE}
require(tidyverse)
require(haven)
require(ggplot2)
require(Hmisc)
require(reshape2)

workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

# Summary Stats for Starting Pops

## Function Declaration
```{r}
require(survey)
weighted.survey.means <- function(init.pop, transition=FALSE) {

@@

## Incidence
```{r}
getIncidenceRate <- function(t, var) {

@@

Handover plots are generated from a Stata script that can be called via a Make rule (`make handovers`).

@@

## Smoking (ASH)
```{r}
FEM_base <- read_dta('output/COMPLETE/ELSA_core_base/ELSA_core_base_summary.dta')
# Smoking prevalence stats
smok.5059 <- 15.2
smok.60p <- 10.2
# FEM summary, filter for 2018 and 60p
#FEM.smok <- FEM_sum
FEM.smok <- FEM_base
FEM.smok <- FEM.smok %>%
                filter(year == 2018) %>%
                select(contains('smoken')) %>%
                select(contains('60p'), contains('5059')) %>%
                select(contains('p_'))
FEM.smok <- FEM.smok * 100
smok.combined <- data.frame(FEM = FEM.smok[1,1], ASH = 10.2)
smok.combined <- data.frame(source = c('FEM', 'FEM', 'ASH', 'ASH'), age = c('50 - 59', '60+', '50 - 59', '60+'), value = c(FEM.smok[1,2], FEM.smok[1,1], 15.2, 10.2))
group.colours <- c(FEM = '#00bfc4', ASH = '#f8766d')
smok.plot <-ggplot(data = smok.combined, aes(x = age, y = value)) +
                geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
                scale_fill_manual(values=group.colours) +
                labs(x = ' ', y = 'Prevalence (%)')

@@

## Heart Disease Intervention

### Death Age
With confidence intervals:
```{r}
b_rep <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_by_rep.dta')
h_rep <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_by_rep.dta')
compareDeathAgeConfints <- function(b, i, int_name=FALSE, save=FALSE, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/') {

@@

@@

### 2022-05-30 FEM_R/OLD_STUFF/IJM_paper1_vis_WIP.Rmd
Lots of WIP and changes for the lockdown_alcohol intervention

>>>>

<!--### Baseline Projections by Subpopulation

```{r echo = FALSE}
visProjectedBySubpop <- function(base, cd, path='/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/Scenario_1/') {

  if(cd == 'cancre') {
    dis <- 'Cancer'
  } else if(cd == 'diabe') {
    dis <- 'Diabetes'
  } else if(cd == 'hearte') {
    dis <- 'Heart Disease'
  }

  # Generate varnames
  all <- paste0('p_', cd, '_all')
  # age
  a5564 <- paste0('p_', cd, '_5564')
  a6574 <- paste0('p_', cd, '_6574')
  a7584 <- paste0('p_', cd, '_7584')
  a85p <- paste0('p_', cd, '_85p')

  ageMelt <- base %>%
              select(c('year', a5564, a6574, a7584, a85p)) %>%
              dplyr::rename('55 to 64' = a5564, '65 to 74' = a6574, '75 to 64' = a7584, '85+' = a85p) %>%
              reshape2::melt(id.var = 'year', value.name = 'Prevalence')

  ggplot(data=ageMelt, aes(x=year, y=Prevalence, color = variable)) +
          geom_line() +
          labs(title = dis, x = 'Year', y = 'Prevalence')
}

visProjectedBySubpop(baseline, cd = 'cancre')
visProjectedBySubpop(baseline, cd = 'diabe')
visProjectedBySubpop(baseline, cd = 'hearte')
```

-->

### 2022-05-30 FEM_R/OLD_STUFF/PH_Sensitivity_vis.Rmd
Lots of WIP and changes for the lockdown_alcohol intervention

ggplot(cohort, aes(x=age, y=a_bmi_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Average BMI by Age', y='Average BMI', x='Age')

@@

pop <- read_dta('output/ELSA_cohort/ELSA_cohort_summary.dta')
ep10 <- read_dta('output/ExstatP10/ExstatC10_summary.dta')
ep50 <- read_dta('output/ExstatP50/ExstatC50_summary.dta')
ep80 <- read_dta('output/ExstatP80/ExstatC80_summary.dta')

# Now plot all survival curves together
ggplot(pop, aes(x=year, y=survival)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Cohort Survival Over Time', y='Survival', x='Age')

ggplot(pop, aes(x=year, y=a_bmi_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Average BMI Over Time', y='Average BMI', x='Age')

ggplot(pop, aes(x=year, y=p_diabe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Prevalence of Diabetes Over Time', y='Prevalence of Diabetes', x='Age')

ggplot(pop, aes(x=year, y=p_hibpe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Prevalence of Hypertension Over Time', y='Prevalence of Hypertension', x='Age')

ggplot(pop, aes(x=year, y=p_hearte_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Prevalence of Heart Disease Over Time', y='Prevalence of Heart Disease', x='Age')

ggplot(pop, aes(x=year, y=p_cancre_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Prevalence of Cancer Over Time', y='Prevalence of Cancer', x='Age')

ggplot(pop, aes(x=year, y=p_stroke_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=dc10, size=0.3, col='green') +
        geom_line(data=dc50, size=0.3, col='blue') +
        geom_line(data=dc80, size=0.3, col='red') +
        labs(title='Prevalence of Stroke Over Time', y='Prevalence of Stroke', x='Age')

>>>>

ggplot(cohort, aes(x=age, y=a_bmi_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Average BMI by Age', y='Average BMI', x='Age')

ggplot(cohort, aes(x=age, y=p_diabe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Prevalence of Diabetes by Age', y='Prevalence of Diabetes', x='Age')

ggplot(cohort, aes(x=age, y=p_hibpe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Prevalence of Hypertension by Age', y='Prevalence of Hypertension', x='Age')

ggplot(cohort, aes(x=age, y=p_hearte_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Prevalence of Heart Disease by Age', y='Prevalence of Heart Disease', x='Age')

ggplot(cohort, aes(x=age, y=p_cancre_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Prevalence of Cancer by Age', y='Prevalence of Cancer', x='Age')

ggplot(cohort, aes(x=age, y=p_stroke_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ec10, size=0.3, col='green') +
        geom_line(data=ec50, size=0.3, col='blue') +
        geom_line(data=ec80, size=0.3, col='red') +
        labs(title='Prevalence of Stroke by Age', y='Prevalence of Stroke', x='Age')

@@

pop <- read_dta('output/ELSA_Baseline/ELSA_Baseline_summary.dta')
ep10 <- read_dta('output/ExstatP10/ExstatP10_summary.dta')
ep50 <- read_dta('output/ExstatP50/ExstatP50_summary.dta')
ep80 <- read_dta('output/ExstatP80/ExstatP80_summary.dta')

# Now plot all survival curves together
ggplot(pop, aes(x=year, y=d_age_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Average Age at Death Over Time', y='Average Age at Death', x='Year')

ggplot(pop, aes(x=year, y=a_bmi_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Average BMI Over Time', y='Average BMI', x='Year')

ggplot(pop, aes(x=year, y=p_diabe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Prevalence of Diabetes Over Time', y='Prevalence of Diabetes', x='Year')

ggplot(pop, aes(x=year, y=p_hibpe_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Prevalence of Hypertension Over Time', y='Prevalence of Hypertension', x='Year')

ggplot(pop, aes(x=year, y=p_hearte_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Prevalence of Heart Disease Over Time', y='Prevalence of Heart Disease', x='Year')

ggplot(pop, aes(x=year, y=p_cancre_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Prevalence of Cancer Over Time', y='Prevalence of Cancer', x='Year')

ggplot(pop, aes(x=year, y=p_stroke_all)) +
        geom_line(col='black', size=0.3) +
        geom_line(data=ep10, size=0.3, col='green') +
        geom_line(data=ep50, size=0.3, col='blue') +
        geom_line(data=ep80, size=0.3, col='red') +
        labs(title='Prevalence of Stroke Over Time', y='Prevalence of Stroke', x='Year')

### 2022-05-30 FEM_R/OLD_STUFF/summary_statistics_forPaper.Rmd
Lots of WIP and changes for the lockdown_alcohol intervention

#bmi.cut <- cut(stock$bmi, breaks = c(20, 25, 30))
```

# Weighted Means
```{r}
weighted.mean(stock$male, stock$weight)

weighted.mean(stock$cancre, stock$weight)
weighted.mean(stock$diabe, stock$weight)
weighted.mean(stock$hearte, stock$weight)
weighted.mean(stock$stroke, stock$weight)
weighted.mean(stock$lunge, stock$weight)
weighted.mean(stock$hibpe, stock$weight)

@@

  if(!transition) {
    design <- svydesign(id = ~idauniq,
                      weights = ~weight,
                      data = init.pop)
  } else if(transition) {
    # Error from missing cwtresp var - drop all that are missing to solve
    init.pop <- init.pop[complete.cases(init.pop$cwtresp),]
    design <- svydesign(id = ~idauniq,
                      weights = ~cwtresp,
                      data = init.pop)
  }
  print(svymean(~age, design, na.rm=TRUE))
  print(svyvar(~age, design, na.rm=TRUE))
  print(svymean(~male, design, na.rm=TRUE))
  print(svymean(~bmi, design, na.rm=TRUE))
  print(svyvar(~bmi, design, na.rm=TRUE))
  print(svymean(~smoken, design, na.rm=TRUE))
  print(svymean(~smokev, design, na.rm=TRUE))
  print(svymean(~hsless, design, na.rm=TRUE))
  print(svymean(~college, design, na.rm=TRUE))
  print('---------------------')
  print(svymean(~cancre, design, na.rm=TRUE))
  print(svymean(~diabe, design, na.rm=TRUE))
  print(svymean(~hearte, design, na.rm=TRUE))
  print(svymean(~stroke, design, na.rm=TRUE))
  print(svymean(~lunge, design, na.rm=TRUE))
  print(svymean(~hibpe, design, na.rm=TRUE))
}

@@

getIncidenceRate(trans, 'cancre')
getIncidenceRate(trans, 'diabe')
getIncidenceRate(trans, 'hearte')
getIncidenceRate(trans, 'stroke')
getIncidenceRate(trans, 'lunge')
getIncidenceRate(trans, 'hibpe')
```

>>>>

#bmi.cut <- cut(stock$bmi, breaks = c(20, 25, 30))

rm(stock.sum)
```

# Weighted Means
```{r}
weighted.mean(stock$male, stock$weight)
print('-------')
weighted.mean(stock$cancre, stock$weight)
weighted.mean(stock$diabe, stock$weight)
weighted.mean(stock$hearte, stock$weight)
weighted.mean(stock$stroke, stock$weight)
weighted.mean(stock$lunge, stock$weight)
weighted.mean(stock$hibpe, stock$weight)
weighted.mean(stock$alzhe, stock$weight)
weighted.mean(stock$demene, stock$weight)
weighted.mean(stock$hchole, stock$weight)

@@

  if(!transition) {
    design <- svydesign(id = ~idauniq,
                      weights = ~weight,
                      data = init.pop)
  } else if(transition) {
    # Error from missing cwtresp var - drop all that are missing to solve
    init.pop <- init.pop[complete.cases(init.pop$cwtresp),]
    design <- svydesign(id = ~idauniq,
                      weights = ~cwtresp,
                      data = init.pop)
  }
  print(svymean(~age, design, na.rm=TRUE))
  print(svyvar(~age, design, na.rm=TRUE))
  print(svymean(~male, design, na.rm=TRUE))
  print(svymean(~bmi, design, na.rm=TRUE))
  print(svyvar(~bmi, design, na.rm=TRUE))
  print(svymean(~smoken, design, na.rm=TRUE))
  print(svymean(~smokev, design, na.rm=TRUE))
  print(svymean(~hsless, design, na.rm=TRUE))
  print(svymean(~college, design, na.rm=TRUE))
  print('---------------------')
  print(svymean(~cancre, design, na.rm=TRUE))
  print(svymean(~diabe, design, na.rm=TRUE))
  print(svymean(~hearte, design, na.rm=TRUE))
  print(svymean(~stroke, design, na.rm=TRUE))
  print(svymean(~lunge, design, na.rm=TRUE))
  print(svymean(~hibpe, design, na.rm=TRUE))
  print(svymean(~alzhe, design, na.rm=TRUE))
  print(svymean(~demene, design, na.rm=TRUE))
  print(svymean(~hchole, design, na.rm=TRUE))
}

@@

getIncidenceRate(trans, 'cancre')
getIncidenceRate(trans, 'diabe')
getIncidenceRate(trans, 'hearte')
getIncidenceRate(trans, 'stroke')
getIncidenceRate(trans, 'lunge')
getIncidenceRate(trans, 'hibpe')
getIncidenceRate(trans, 'alzhe')
getIncidenceRate(trans, 'demene')
getIncidenceRate(trans, 'hchole')
```
